Blocking-resistant communication\\through domain fronting

### 2014-08-01 docs/meek.tex
Spellcheck.

% >>> (1*543+450.)/(1*543)
% 1.828729281767956
% >>> (2*543+450.)/(2*543)
% 1.4143646408839778
% >>> (3*543+450.)/(3*543)
% 1.276243093922652
\noindent
The total overhead varies according to the length
of the Host field and the specifics of the intermediate web service's TLS,
but is somewhere in the neightborhood of $(543+450)/543-1\approx83$\%.
This is the worst case, when Tor sends a single cell.
Tor can bunch multiple cells into one transmission;
if two cells are sent at once, the overhead drops to
${\approx}41$\%; if three, it is ${\approx}28$\%.
Bulk uploads and downloads tend to bunch many cells at once.
Persistent HTTP connections as used by Psiphon reduce overhead further,
because only one HTTP header is sent for a large number of transmissions.
Empty polling requests also use bandwidth,
but they are sent only when the connection is idle
so they don't affect upload or download speed.
As is discussed in Section~\ref{sec:trafficanalysis},
\meekclient\ reuses the same TLS connection for many requests,
so the fixed overhead of the initial TLS handshake is amortized.

@@

Domain fronting derives part of its unblockability from the
high collateral damage of blocking the domain fronted through.
Fronting through \urll{www.google.com} to App Engine, for example,
is betting that censor will lack the temerity to block Google.
The Great Firewall of China called our bluff in June of 2014,
when it blocked access to all Google services~\cite{cn-google-block}.
In 2012, the government of Pakisten blocked to all of YouTube
in order to restrict access to one video,
and in 2011, the government of Egypt briefly ``turned off the net'' completely.
% http://www.washingtonpost.com/business/economy/youtube-blocked-in-pakistan/2012/09/17/30081fa2-00ea-11e2-b257-e1c2b3548a4a_story.html
% https://en.wikipedia.org/wiki/Internet_censorship_in_Egypt#2011_Internet_shutdown
These examples show that blocking resistance is not an absolute,
black-and-white security property;
it can only be discussed in an economic context, relative to the costs borne
by the censor and by users of a system.
To block Google is an extreme measure,
probably out of reach of most censors.
Blocking all of the fronting-capable services listed in
Section~\ref{sec:survey} would be even harder.

@@

meek's use of HTTPS is subject to the usual public key infrastructure
and trust model.
The browser running the HTTPS camouflage extension (Section~\ref{sec:browserextension})
has a standard list of trusted certificate authorities.
A censor that controls a certificate authority trusted by the browser
would be able to do a man-in-the-middle attack
between the client and the intermediate web service,
and detect fronting by decrypting HTTP requests and checking for specific Host headers.
Such a censor would be able to detect circumvention,
but still not read the client's plaintext because of the
additional encryption and authentication of the tunneled Tor layer.
It seems risky for the censor to risk being detected in
ia man-in-the-middle attack merely to confirm that a user is circumventing,
but it is not impossible for a sufficiently powerful censor.
The problem doesn't exist when the front domain is one
that happens have its public key ``pinned'' in the headless browser,
for instance when using the Chrome extension and fronting through
\urll{www.google.com}.

>>>>

% >>> (1*543+450.)/(1*543)
% 1.828729281767956
% >>> (2*543+450.)/(2*543)
% 1.4143646408839778
% >>> (3*543+450.)/(3*543)
% 1.276243093922652
\noindent
The total overhead varies according to the length
of the Host field and the specifics of the intermediate web service's TLS,
but is somewhere in the neighborhood of $(543+450)/543-1\approx83$\%.
This is the worst case, when Tor sends a single cell.
Tor can bunch multiple cells into one transmission;
if two cells are sent at once, the overhead drops to
${\approx}41$\%; if three, it is ${\approx}28$\%.
Bulk uploads and downloads tend to bunch many cells at once.
Persistent HTTP connections as used by Psiphon reduce overhead further,
because only one HTTP header is sent for a large number of transmissions.
Empty polling requests also use bandwidth,
but they are sent only when the connection is idle
so they don't affect upload or download speed.
As is discussed in Section~\ref{sec:trafficanalysis},
\meekclient\ reuses the same TLS connection for many requests,
so the fixed overhead of the initial TLS handshake is amortized.

@@

Domain fronting derives part of its unblockability from the
high collateral damage of blocking the domain fronted through.
Fronting through \urll{www.google.com} to App Engine, for example,
is betting that censor will lack the temerity to block Google.
The Great Firewall of China called our bluff in June of 2014,
when it blocked access to all Google services~\cite{cn-google-block}.
In 2012, the government of Pakistan blocked to all of YouTube
in order to restrict access to one video,
and in 2011, the government of Egypt briefly ``turned off the net'' completely.
% http://www.washingtonpost.com/business/economy/youtube-blocked-in-pakistan/2012/09/17/30081fa2-00ea-11e2-b257-e1c2b3548a4a_story.html
% https://en.wikipedia.org/wiki/Internet_censorship_in_Egypt#2011_Internet_shutdown
These examples show that blocking resistance is not an absolute,
black-and-white security property;
it can only be discussed in an economic context, relative to the costs borne
by the censor and by users of a system.
To block Google is an extreme measure,
probably out of reach of most censors.
Blocking all of the fronting-capable services listed in
Section~\ref{sec:survey} would be even harder.

@@

meek's use of HTTPS is subject to the usual public key infrastructure
and trust model.
The browser running the HTTPS camouflage extension (Section~\ref{sec:browserextension})
has a standard list of trusted certificate authorities.
A censor that controls a certificate authority trusted by the browser
would be able to do a man-in-the-middle attack
between the client and the intermediate web service,
and detect fronting by decrypting HTTP requests and checking for specific Host headers.
Such a censor would be able to detect circumvention,
but still not read the client's plaintext because of the
additional encryption and authentication of the tunneled Tor layer.
It seems risky for the censor to risk being detected in
a man-in-the-middle attack merely to confirm that a user is circumventing,
but it is not impossible for a sufficiently powerful censor.
The problem doesn't exist when the front domain is one
that happens have its public key ``pinned'' in the headless browser,
for instance when using the Chrome extension and fronting through
\urll{www.google.com}.
